Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-10-31 paper/pool_model.tex
use documentclass from folder
fix typo in image name

% \documentclass[10pt,A4paper]{article}
\documentclass[10pt,twocolumn,5p]{elsarticle}
\usepackage[utf8]{inputenc}

@@

        \includegraphics[width=\textwidth]{Figures-abm-homogeneous-images-snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures-abm-homogeneous-low-diffusion-images-snapshot_00012000.png}

>>>>

% \documentclass[10pt,A4paper]{article}
\documentclass[10pt,twocolumn,5p]{elsarticle/elsarticle}
\usepackage[utf8]{inputenc}

@@

        \includegraphics[width=\textwidth]{Figures-abm-homogenous-images-snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures-abm-homogenous-low-diffusion-images-snapshot_00012000.png}
